---
title: "Case Study"
output: html_document
---

```{r, include = FALSE, message = FALSE, warning = FALSE}
library(tidyverse)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

Load key packages.

```{r}
library(p8105.datasets)
library(leaflet)

data(nyc_airbnb)
```


## Brainstorm questions

* Pick a neighborhood / borough, investigate price
  * If we had dates, does that affect price?
* Does the type of unit affect rating / price?
* What about ZIP codes?
* What rental has the highest reviews?
* Are there any connections between price and other variables?
* What about prices over time?
  * Could we look at prices before and after the pandemic?
* How else did the pandemic affect AirBNB in NYC?
* Does the name of the rental affect the price / rating?
* What does the number of days available have to do with anything else?


Let's look at prices first

```{r}
nyc_airbnb |> 
  drop_na(price) |> 
  group_by(neighbourhood_group) |> 
  summarize(
    mean_price = mean(price),
    min_price = min(price),
    max_price = max(price)
  )

```

What about room type in a given neighborhood?

```{r}
nyc_airbnb |> 
  drop_na(price) |> 
  group_by(room_type,neighbourhood_group) |> 
  summarize(
    mean_price = mean(price)
  ) |> 
  pivot_wider(
    names_from = room_type,
    values_from = mean_price
  )
```


```{r}
nyc_airbnb |> 
  count(neighbourhood_group, room_type)
```


Make some plots

```{r}
nyc_airbnb |> 
  ggplot(aes(x = price)) + 
  geom_histogram() +
  facet_grid(room_type ~ neighbourhood_group)+
  scale_x_continuous(limits = c(0, 1000))
```


```{r}
nyc_airbnb |> 
  filter(
    neighbourhood_group == "Manhattan",
    price < 500, 
    room_type == "Entire home/apt") |> 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) |> 
  ggplot(aes(x = neighbourhood, y = price)) +
  geom_violin() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))
```




(remember to look at extreme values ...)

```{r}
nyc_airbnb |> 
  filter(price > 9000)
```


```{r}
nyc_airbnb |> 
  filter(calculated_host_listings_count > 30)
```



Keep looking at location

```{r}
nyc_airbnb |> 
  filter(
    neighbourhood_group == "Manhattan",
    price < 1000, 
    room_type == "Entire home/apt") |> 
  ggplot(aes(x = lat, y = long, color = review_scores_location)) + 
  geom_point()
```


can we make a better map

```{r}
pal <- colorNumeric(
  palette = "viridis",
  domain = nyc_airbnb$review_scores_location)


nyc_airbnb |> 
  filter(
    neighbourhood_group == "Manhattan",
    room_type == "Entire home/apt") |> 
  leaflet() |> 
  addProviderTiles(providers$CartoDB.Positron) |> 
  addCircleMarkers(
    ~lat, ~long, 
    color = ~pal(review_scores_location),
    radius = 2)
```



